\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs,bm}
\usepackage{natbib}
\usepackage{graphicx}
%\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\doublespacing

\addtolength{\belowcaptionskip}{4pt}
\DeclareMathOperator*{\argmax}{argmax}

\title{Quiz 2}
\author{Name:}% Put your name here

\begin{document}

\maketitle

\section{Weighted least squares}
The data (\texttt{wls.txt}) have two variables $x$ and $y$. There is a weight vector \texttt{w}

\begin{enumerate}
\item Read the data into an R session.
\item Draw the scatter plot of the data.
\item Write down a linear regression model for the data. Be careful because there is a weighted least squares example.
\item Fit the model and present a summary for the coefficients.
\item Present the anova table.
\item Draw the regression line and 99\% point-wise confidence bands with $X$ in its range.
\end{enumerate}


\section{Polynomial regression}

The data (\texttt{poly.txt}) have two variables: $x$, $y$.


\begin{enumerate}
\item Read the data into an R session.
\item Write down a linear regression model for the data.
\item Fit the simple linear model and present a summary for the coefficients.
\item Fit the quadratic model and present a summary for the coefficients.
\item Fit the cubic model and present a summary for the coefficients.
\item Present the anova tables for three fitted models.
\item Present the scatter plot and draw three regression curves.
\item Choose the model that seems appropriate and justify your choice.
\end{enumerate}


\appendix
\begin{verbatim}
%Put your R codes here!
\end{verbatim}
\end{document}
